---
title: "Lab 2"
author: "Anisha, Diana, Dillon, Futing, Ian"
date: "5/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

### Q1:

A. Three fundamental components of a function are the:

1. Formals: Arguments supplied to a function;

2. Body: The code within the functions, and;

3. Environment: The data structure that maps how the function finds the values associated with each variable or name.

B. Three ways functions can be stored/applied:

1. Stored in an object (named). Useful when fundamental/having various uses, so that you want to call it concisely and define it eslewhere.

2. Anonymously, where the function isn't bound to a name. Can be appeaing, perhaps, when used within a loop

3. Stored in a list, which then lets you loop through each function in the list simply.


```{r Part B, Q1}
warningNA <- function(x) {
  if(sum(is.na(x)) != 0) {
    warning(
      sum(is.na(x)),
      " NAs in vector removed",
      call. = FALSE
    )
  }
}

meanCalc <- function(x) {
  newVector <- x[!is.na(x)]
  sumVector <- sum(newVector)
  meanVector <- sumVector / length(newVector)
  meanVector
}

meanWarning <- function(x) {
    warningNA(x)
    meanCalc(x)
}

check <- c(NA, NA, 3, 3, 10, 2)
meanWarning(check)

```

```{r Part B, Q2}
testVec <- c(-1000230, -102, -37, -22, -7, -5, -1, NA, NA, 0, 1, 5, 7, 16, 22, 37, 102, 1000230) #Test vector with NAs and larger numbers. Mean is 1 if NAs are removed
warningNA(testVec) #we test here to see if 2 NAs are removed with the warningNA function
meanCalc(testVec) #check the meanCalc function
base::mean(testVec, na.rm = TRUE) #compare base mean against our function
meanWarning(testVec)
base::mean(testVec, na.rm = TRUE)==meanWarning(testVec) #make extra sure they're the same
```


```{r Part B, Q4}
only_numeric <- function(df){
  df %>% 
    select_if(is.numeric)
  
  
}


only_numeric(mtcars)


```

```{r Part B, Q5}
only_numeric_summary <- function(df){
  df_numeric <- only_numeric(df)
  if (length(df_numeric)!=0) {
    if (length(df_numeric)!=length(df)){
      warning("The columns are omitted because they are non-numeric:\n",
              paste(names(df%>%select(which(!colnames(df) %in% colnames(df_numeric)))),
                    collapse=","))
    }
    df_numeric %>%
      pivot_longer(everything(),
                   names_to = "var",
                   values_to = "val") %>%
      group_by(var) %>%
      summarise(mean = mean(val, na.rm = TRUE),
                sd = sd(val, na.rm = TRUE))
  }
  else{
    return("All columns are non-numeric")
  }
}

only_numeric_summary(mtcars)
only_numeric_summary(forcats::gss_cat)
only_numeric_summary(forcats::gss_cat["marital"])
```

