---
title: "notes"
author: "Anisha, Diana, Dillon, Futing, Ian"
date: "5/13/2022"
output: html_document
---

# General Notes

Here are some code snippets that should help with the final...

## Specific Comments

I've set up the other file to create a table of contents based on sections - single hashtags for section headers and double hashtags for subsections. Make sure that code snippets don't go over 80 characters as they'll run off the page 


# Demographics
Useful code from the tableby package

```{r, eval = FALSE}
library(tableby)

labels(demog_dat)  <- c(age = 'Age', sex = "Gender", 
                        ethnic_cat = "Race", education = "Education")
demog_tab <- summary(tableby(~ age + sex + ethnic_cat + education, 
                             data = demog_dat, test = FALSE),  
                     title = "Full Sample Demographics")
demog_tab

demog_tab_group <- summary(tableby(list(sex, agegroup_fac) ~ 
                                     age + sex + ethnic_cat + education, 
                                   data = demog_dat, test = FALSE), 
                           title = "Grouped Sample Demographics") 

demog_tab_group
```


# Scoring Scales
The psych package has a function that will score scales if you give it a key - the key for the ipip items are downloading from the dataverse website...here's code i have that does this for a different project

https://personality-project.org/r/psych/help/score.items.html
```{r, eval = FALSE}

items <-  as.list( key %>% select(facet, item_id) %>% 
  pivot_wider(names_from = facet, values_from = item_id  ))

factor_items <- as.list( key %>% select(factor, item_id) %>% 
  pivot_wider(names_from = factor, values_from = item_id  ))

key <- key %>% 
  mutate(reversed_new =
         case_when(
           reversed == FALSE ~ "", 
           TRUE ~ "-"), 
         codes = paste(reversed_new, item_id, sep = ""))

scales <-   key %>% select(facet, codes) %>% 
  pivot_wider(names_from = facet, values_from = codes  )

factor_scales <-   as.list( key %>% select(factor, codes) %>% 
  pivot_wider(names_from = factor, values_from = codes  ))

key_unlist <- list(
                 Anhedonia = unlist(scales$Anhedonia), 
                 Anxiousness = unlist(scales$Anxiousness), 
                 AttentionSeeking = unlist(scales$`Attention Seeking`), 
                 Callousness= unlist(scales$Callousness), 
                 Deceitfulness = unlist(scales$Deceitfulness), 
                 Depressivity = unlist(scales$Depressivity), 
                 Distractability = unlist(scales$Distractibility), 
                 Eccentricity = unlist(scales$Eccentricity), 
                 EmotionalLability = unlist(scales$`Emotional Lability`), 
                 Grandiosity = unlist(scales$Grandiosity), 
                 Hostility = unlist(scales$Hostility), 
                 Impulsivity = unlist(scales$Impulsivity),
                 IntimacyAvoidance = unlist(scales$`Intimacy Avoidance`), 
                 Irresponsibility = unlist(scales$Irresponsibility), 
                 Manipulativeness = unlist(scales$Manipulativeness), 
                 PerceptualDisregulation = unlist(scales$`Perceptual Dysregulation`), 
                 Perseveration = unlist(scales$Perseveration), 
                 RestrictedAffectivity = unlist(scales$`Restricted Affectivity`),
                 RigidPerfectionism = unlist(scales$`Rigid Perfectionism`), 
                 RiskTaking = unlist(scales$`Risk Taking`), 
                 SeparationAnxiety = unlist(scales$`Separation Insecurity`), 
                 Submissiveness = unlist(scales$Submissiveness), 
                 Suspiciousness = unlist(scales$Suspiciousness), 
                 UnusualBeliefs = unlist(scales$`Unusual Beliefs & Experiences`), 
                 Withdrawal = unlist(scales$`Withdrawal`), 
                 Detachment = unlist(factor_scales$`Detachment`), 
                 Disinhibition = unlist(factor_scales$Disinhibition), 
                 Psychoticism = unlist(factor_scales$Psychoticism), 
                 NegativeAffect = unlist(factor_scales$`Negative Affect`), 
                 Antagonism = unlist(factor_scales$Antagonism), 
                 Schizotypal = c(unlist(items$`Percentual Dysregulation`), 
                                 unlist(items$`Unusual Beliefs & Experiences`),
                                 unlist(items$Eccentricity), 
                                 unlist(items$`Restricted Affectivity`), 
                                 unlist(items$Withdrawal), 
                                 unlist(items$Suspiciousness)), 
                 Antisocial = c(unlist(items$Manipulativeness), 
                                unlist(items$Callousness), 
                                unlist(items$Deceitfulness), 
                                unlist(items$Hostility), 
                                unlist(items$`Risk Taking`), 
                                unlist(items$Impulsivity), 
                                unlist(items$Irresponsibility)), 
                 Borderline = c(unlist(items$`Emotional Lability`), 
                                unlist(items$Anxiousness), 
                                unlist(items$`Separation Insecurity`), 
                                unlist(items$Depressivity), 
                                unlist(items$Impulsivity), 
                                unlist(items$`Risk Taking`), 
                                unlist(items$Hostility)), 
                 Narcissistic = c(unlist(items$Grandiosity), 
                                  unlist(items$`Attention Seeking`)), 
                 Avoidant =     c(unlist(items$Anxiousness), 
                                  unlist(items$Withdrawal), 
                                  unlist(items$Anhedonia), 
                                  unlist(items$`Intimacy Avoidance`)), 
                 OCPD =         c(unlist(items$`Rigid Perfectionism`), 
                                  unlist(items$Perseveration), 
                                  unlist(items$`Intimacy Avoidance`), 
                                  unlist(items$`Restricted Affectivity`))
                 )



pid_raw_comp2 <- cbind(pid_sub, psych::scoreItems(key_unlist, pid_sub, 
                       min=1, max=6, totals = FALSE, impute = "none")$scores)


          
```

# Descriptives Tables

We wont want the same contents of the tables, but here's code that will create nice looking tables - idk if we'll need the "add_header_above" commend...but it's helpful sometimes

note that in the code options results = 'asis'

```{r, eval = FALSE, results = 'asis'}
kable(
  full_facet_descriptives,
  booktabs = TRUE,
  longtable = TRUE,
  #escape = FALSE,
  col.names = c("Scale", "N", "Mean", "SD", "Mean", "SD", 
                "Perc. 1", "Perc. 2", "Perc. 3", 
                "Perc. 4", "Perc. 5", "Perc. 6", 
                "Perc. 1", "Perc. 2", "Perc. 3", 
                "Perc. 4", "Perc. 5"),
  caption = "Scale Norms"
  ) %>% 
  landscape() %>% 
  kable_styling(font_size = 6, 
                latex_options = c("scale_down", "repeat_header")) %>% 
  kable_classic() %>% 
  add_header_above(c(" " = 2, "Unweighted" = 2, 
                     "Weighted" = 2, "Normal" = 6, "Empirical" = 5))


```


## Grouped Descriptives tables

probably should do this in something other than a loop...wrote this code before taking this class
```{r, results = 'asis', eval = FALSE}
grouped_facet_descriptives <- map(grouped_facet_descriptives,
   ~select(., item, n, mean, sd, contains("norm"), contains("ecdf")) %>% 
    `rownames<-`( NULL )  %>% 
  mutate(across(where(is.numeric), round, 2)))


for(i in 1:length(grouped_facet_descriptives)){
  
print(grouped_facet_descriptives[[i]] %>% 
kable(
  booktabs = TRUE,
  longtable = TRUE,
  #escape = FALSE,.c
  col.names = c("Item", "N", "Mean", "SD", 
                "Perc. 1", "Perc. 2", "Perc. 3", 
                "Perc. 4", "Perc. 5", "Perc. 6", 
                "E. Perc. 1", "E. Perc. 2", "E. Perc. 3", 
                "E. Perc. 4","E. Perc. 5"),
  caption = paste("Scale Norms", names(item_descriptives[i]), sep = ": ")
  ) %>% 
  landscape() %>% 
  kable_styling(font_size = 7, latex_options = c("repeat_header")) %>% 
  kable_classic() %>% 
  add_header_above(c(" " = 4, "Normal" = 6, "Empirical" = 5))
)}
```


# Parallel Analysis

this is where we actually examine the factor structure of the data - we should do this once in the whole sample and once in the nested data

we'll want to extract model results here...i'll leave it up to you what all to extract but number of factors is what we're most interested in
```{r, eval = FALSE}
pid_item_cov <- cov(raw_pid)

parallel <- fa.parallel(pid_item_cov, n.iter = 20, cor = "cov") 
plot(parallel$fa.values[1:10])




```

```

