---
title: "The Personality Structures of the 50 States"
author: "Anisha Babu, Diana DeWald, Ian Shryock, Dillon Welindt, Futing Zou"
output: 
  bookdown::pdf_document2:
    toc: TRUE
    lof: TRUE
    lot: TRUE
    extra_dependencies: ["tocbibind"]
always_allow_html: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(dataverse)
library(kableExtra)
library(psych)

# download data from url
Sys.setenv("DATAVERSE_SERVER" = "dataverse.harvard.edu")
SAPA <- get_dataframe_by_name(
  "sapaTempData04apr2006thru18aug2010.tab",
  "10.7910/DVN/H9RQD6")

# IPIP keys list
IPIPkeysList <- list(
IPIP100agreeableness = c("-q_140", "-q_146", "q_150", "-q_195", "-q_200", "q_217", "-q_838", "q_844", "q_1041", "q_1053", "q_1162", "-q_1163", "q_1206", "q_1364", "q_1385", "q_1419", "q_1705", "q_1763", "q_1792", "q_1832"),
IPIP100conscientiousness = c("q_76", "q_124", "q_530", "q_619", "-q_626", "-q_904", "q_931", "q_962", "-q_1254", "-q_1255", "q_1290", "q_1333", "q_1374", "-q_1397", "q_1422", "-q_1452", "-q_1483", "q_1507", "-q_1696", "-q_1949"),
IPIP100extraversion = c("-q_241", "q_254", "q_262", "-q_403", "-q_690", "q_698", "-q_712", "q_815", "q_819", "-q_901", "-q_1114", "-q_1180", "q_1205", "q_1410", "-q_1480", "q_1742", "q_1768", "q_1803", "-q_1913"),
IPIP100intellect = c("q_128", "q_132", "-q_194", "q_240", "-q_316", "q_422", "q_492", "q_493", "-q_609", "q_1050", "q_1058", "-q_1083", "-q_1088", "q_1090", "q_1388", "q_1392", "q_1738", "-q_1861", "q_1893", "-q_1964"),
IPIP100stability = c("-q_108", "q_177", "q_248", "-q_497", "-q_890", "-q_952", "-q_960", "-q_974", "-q_979", "-q_986", "-q_995", "-q_1020", "-q_1099", "-q_1479", "-q_1505", "q_1585", "q_1677", "q_1683", "-q_1775", "-q_1989"),
IPIP50agreeableness = c("q_844", "q_1792", "q_1763", "q_150", "q_1419", "q_1053", "-q_838", "-q_200", "-q_195", "-q_1163"),
IPIP50conscientiousness = c("-q_1255", "-q_1397", "-q_1483", "-q_1696", "q_124", "q_1290", "q_1507", "q_76", "q_931", "q_962"),
IPIP50extraversion = c("q_819", "q_698", "q_262", "q_1803", "q_1742", "-q_712", "-q_690", "-q_241", "-q_1180", "-q_1114"),
IPIP50intellect = c("q_128", "q_240", "q_1893", "q_1738", "q_1090", "q_1058", "q_1050", "-q_609", "-q_194", "-q_1088"),
IPIP50stability = c("-q_108", "-q_1099", "-q_1479", "-q_1989", "-q_497", "-q_974", "-q_986", "-q_995", "q_1677", "q_248")
)

```

```{r preprocessing, warning = FALSE}
SAPA <- SAPA %>%
  # filter in US
  filter(country == "USA") %>%
  # filter 50 states
  filter(!state %in% c('District of Columbia', 'Guam', 'Palau','Puerto Rico', 'Virgin Islands',
                       'Northern Mariana Islands', 'American Samoa', 'Marshall Islands', NA)) 

# filter out rows with all NA
SAPA <- SAPA[rowSums(is.na(SAPA)) < 99, ]

# in list form select only used Q's
usedQ <- colnames(SAPA[8:106])
IPIPkeys <- map(IPIPkeysList, function(x) {
    x[match(usedQ, x)]
    na.omit(x)
})
# select only IPIP 100
IPIPkeys <- IPIPkeys[1:4]

```

```{r demographics, warning= FALSE}
# idk if this is what we want here - tableby package not available
map((SAPA[c(2,3,5,6,7)]), table)

```

```{r individual subject scores, warning= FALSE}
# score items
scores <- psych::scoreItems(keys = IPIPkeys, items = SAPA, min=1, max=6, totals = FALSE, impute = 'none')$scores


```

```{r #3 descriptives statistics, warning = FALSE, results = 'asis'}
# PEER REVIEW: Move this to the top 
library(arsenal)

#Move package up to the top

# demographic table
demog_tab <- summary(tableby(~ age + gender + race + education, 
                             data = SAPA, test = FALSE),  
                     title = "Full Sample Demographics")
demog_tab

# PEER REVIEW: To get a more elegant table, perhaps you can create your own function that gives you the sample size and percent of sample size by different characteristic and then use map to create a data frame with the categories of choice. I wrote a function below to get you started.

sample <- function(df,x) {
  df %>%
  group_by({{x}}) %>%
  summarize(group_sample = n()) %>%
  ungroup() %>%
  rename(group = {{x}}) %>%
  mutate(total_sample = sum(group_sample),
         percent_sample = group_sample/total_sample) %>%
  select(group,group_sample, percent_sample)
}

sample(SAPA,race)
sample(SAPA,education)

# to add for final: demographic table grouped by state

# to add for final:  improve correlation matrix format/names (below), include other personality traits (like stability), and include more complex grouping by state, gender, race, etc.


res <- cor(scores, use = "complete.obs")
round(res, 2)

library(apaTables)

apa.cor.table(scores, filename="Corr_table.doc", show.conf.interval=F)
```

```{r #4 average scores by factor, warning = FALSE}

# average scores on included survey questions
average_surveyscores <- SAPA %>%
  summarize_at(vars(q_76:q_1989), mean, na.rm = TRUE)


# average scores on survey questions by state (for final: can group by other variables as well)
average_statescores <- SAPA %>%
  group_by(state) %>%
  summarize_at(vars(q_76:q_1989), mean, na.rm = TRUE)

```

```{r #5 factor structure}

```

```{r #6/7 state-wise descriptives, warning = FALSE, results='hide'}
# combine demographics & traits
factorSAPA <- cbind(SAPA[1:7], scores)

# nest data by state
by_state <- split(factorSAPA, factorSAPA$state)

# descriptive stats - THERE SHOULD BE A BETTER WAY TO DO THIS (SOME KIND OF NESTED MAP FXN?)  ## summarize_at?
stateAgree <- map(by_state, ~summarize(.x, meanFactor = mean(IPIP100agreeableness, na.rm = TRUE),
                                    sdFactor = sd(IPIP100agreeableness, na.rm = TRUE),
                                    nFactor = length(IPIP100agreeableness)))
stateCons <- map(by_state, ~summarize(.x, meanFactor = mean(IPIP100conscientiousness, na.rm = TRUE),
                                    sdFactor = sd(IPIP100conscientiousness, na.rm = TRUE),
                                    nFactor = length(IPIP100conscientiousness)))
stateExtra <- map(by_state, ~summarize(.x, meanFactor = mean(IPIP100extraversion, na.rm = TRUE),
                                    sdFactor = sd(IPIP100extraversion, na.rm = TRUE),
                                    nFactor = length(IPIP100extraversion)))
stateIntel <- map(by_state, ~summarize(.x, meanFactor = mean(IPIP100intellect, na.rm = TRUE),
                                    sdFactor = sd(IPIP100intellect, na.rm = TRUE),
                                    nFactor = length(IPIP100intellect)))
# group all factors in list
allFactor = list(stateAgree, stateCons, stateExtra, stateIntel)
names(allFactor) = c('Agreeableness', 'Conscientiousness', 'Extraversion', 'Intellect')

# function to create table - SHOULD FIND A WAY TO CAPTION EACH TABLE BY STATE & FACTOR
makeTable <- function(x) {
  kable(x, booktabs = TRUE, longtable = TRUE, col.names = c("Mean", "SD", "N"), 
        caption = paste('State of ', x, ' Descriptives')) %>% 
    landscape() %>% 
    kable_styling(font_size = 12, latex_options = c("scale_down", "repeat_header")) %>% 
    kable_classic() 
}

# create tables for each factor & state
map(allFactor, ~map(.x, ~makeTable(.x)))

# PEER REVIEW: I'm not 100% sure what your end goal is. If your trying to create summary statistics for all your factors for each state, I think you can use map_df and split the allFactor list so that you can end up with a nice data frame with a row for each state and summary statistics as columns. Then I can imagine you could use something like the gt package to create a table with color coded cells that show high and low mean scores. Below is a not so very elegan way that you can get there. 

state_factor <- tibble(
  state_names = names(stateAgree),
  agree_factor = map_df(stateAgree,~.x[1]),
  cons_factor = map_df(stateCons,~.x[1]),
  extra_factor = map_df(stateExtra,~.x[1]),
  intel_factor = map_df(stateExtra,~.x[1])
)



```

```{r #8 average scores by factor - from nested states}


```

```{r #9 factor structure - from nested states, include = FALSE, warning = FALSE}
by_stateFactors <- split(SAPA, factorSAPA$state)

stateFactor <- map(by_stateFactors, ~fa.parallel(cov(.x[,8:106], use = "pairwise.complete.obs"), n.iter = 20, cor = "cov")$nfact)
stateFactordf <- as.data.frame(stateFactor)

```

```{r #9 table, warning = FALSE}
stateFactordf
```

# Introduction

## Big Five 
One of the most widely replicated findings within the field of personality psychology is the Big Five structure of personality. With roots in the 1800’s, personality psychology sought to determine the best way to represent the large number of personality traits in a concise structure. This research initially involved researchers providing participants with large numbers of trait descriptive adjectives and asking them to rate the extent to which those adjectives characterize themselves or someone they knew. Dimension reduction analyses were then used to create a simpler structure from those responses. 

Multiple research groups began converging on the five factor structure as early as the 1960’s, with an increasing consensus by the late 1980’s. Most of the recent work on the big five has been conducted through a combination of confirmatory factor analysis and theory driven selection of survey items based on previous findings about the structure. 




## Geographical Personality
In recent years, there has been increasing focus on regional variation of personality traits within the United States. Work has examined the extent to which regions of the US differ on the Big Five domains and can be said to have distinct and characteristic combinations of trait levels. For example, Rentfrow and colleagues (2013) show that the south and midwest are best characterized as friendly and conventional, whereas the west is relaxed and creative, and the northeast is temperamental and uninhibited. 

A limitation of this work is that it examines the extent to which the five factor structure captures each region and what differences in the levels of each factor are due to regional variation. This research utilizes confirmatory factor analyses that assume that the five factor structure is the ideal level of dimensionality to characterize all regions. 

## Cross Cultural Studies
Much of the cross-cultural work on personality structure has found some support for the notion that the five factor structure has applicability in a number of cultures. However, these studies typically are conducted from an etic perspective that translate the items used in western samples. 

However, when studies are conducted from an emic perspective – that is, using trait descriptive adjectives from the language of the culture, rather than translations of items used in the big five framework – different structures emerge. A varying number of factors have been found to best fit different cultures, ranging from one to seven in many cases.




## Geographical Factor Structure within US
Within the US, the regional variation in factor structures has not been an extensively studied topic. Because most research operates within a framework that utilizes confirmatory factor analysis, there is little information on the extent to which regions differ in their factor structure. 

In the current study, we use exploratory factor analyses to provide estimates of the optimal factor structures for each of the fifty states. 


# Brief Methods

## Measures
The International Personality Item Pool is an open-source repository of personality trait items that have been researched extensively in the big five tradition. The current study uses ninety nine of one hundred items from the IPIP-100. Participants rated themselves on a number of personality traits from 1- not at all like me to 6- very much like me. 

## Data Collection
Data were obtained from the Harvard [Dataverse](https://dataverse.harvard.edu/dataverse/SAPA-Project). Data were initially collected using the Synthetic Aperture for Personality Assessment  (Revelle et al., 2016; Condon and Revelle, 2014; Wilt et al., 2011) which utilizes a massively missing completely at random design, wherein each participant only provides responses to a fraction of items. 


# Analyses

First, we provide descriptive norms for the entire US sample, and then by state. 

Next, we use parallel analysis to determine the optimal number of factors in the whole sample. Our hypothesis is that five factors will provide an optimal fit. 

The main analyses are fifty parallel analyses, one for every state, that estimates the optimal number of personality dimensions for each state. We hypothesize that there will be variation in the number of ideal dimensions across states. 


\renewcommand{\thetable}{S\arabic{table}} 
\renewcommand{\thefigure}{S\arabic{figure}}



\definecolor{fancyTextColor}{HTML}{4284f5}
\definecolor{hightlightColor}{HTML}{FFFF66}

\newpage

\listoftables

\newpage

\listoffigures

\newpage



